Introduction to Moltres: an Application for Simulation of Molten Salt Reactors

### 2017-04-17 Moltres.tex
deleting words for brevity

Molten salt reactors are a reactor concept that received considerable interest
in the 1950s and 60s with development of the \gls{ARE} and
later the \gls{MSRE} at \gls{ORNL}. With the inclusion of the \gls{MSR} in the
Generation-IV reactor designs, the reactor concept has gained renewed research
interest in the past decade. Some of the advantages offered by the \gls{MSR}
include lower fissile inventories, no radiation damage constraint on attainable
fuel burn-up, no spent nuclear fuel, no requirement to fabricate and handle
solid fuel, and a homogeneous isotopic composition of fuel in the
reactor \cite{noauthor_gen_2008}. These characteristics give the \gls{MSR} a
potentially unique capability for actinide burning and extension of fuel
resources.

>>>>

Molten salt reactor concepts received considerable interest
in the 1950s and 60s with development of the \gls{ARE} and
later the \gls{MSRE} at \gls{ORNL}. With the inclusion of the \gls{MSR} in the
Generation-IV reactor designs, the reactor concept has gained renewed research
interest in the past decade. Some of the advantages offered by the \gls{MSR}
include lower fissile inventories, no radiation damage constraint on attainable
fuel burn-up, no spent nuclear fuel, no requirement to fabricate and handle
solid fuel, and a homogeneous isotopic composition of fuel in the
reactor \cite{noauthor_gen_2008}. These characteristics give the \gls{MSR} a
potentially unique capability for actinide burning and extension of fuel
resources.
